---
title       : Data Products Assignment Project
subtitle    : Design and Performance of automobiles
author      : Simon
job         : Student Developing data products cours
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---
## Introduction

 * Data from 1974 Motor Trend US Magazine to compare 10 aspects of automoile design
   and performance is stored in mtcars data

*  Data consists of design and pertormance of 32 automobile during the year(1973-74)

*  The variables  are as follows
       1  Miles/(US) gallon
       2  Number of cylinder
       3  Displacement (cu.in.)
       4  Gross horsepower
       5  Rear axle ratio
       6  Weight (lb/1000)
       7  1/4 mile time
       8  V/S
       9  Transmission (0 = automatic, 1 = manual)
       10 Number of forward gears
       11 Number of carburetors


--- .class #id 

## Data Summary

#### Summary of the data objects 

```{r,echo=FALSE}
library(datasets)

dim(mtcars)

summary(mtcars)

```

--- .class #id 

## Regression model

#### Estimate the relationship the exists between the dependent variable and exploratory variable
```{r,echo=FALSE}

fit <- glm(mpg~.,data=mtcars)

summary(fit)

```




--- .class #id 


## Residual Summary

```{r,echo=FALSE}

gfit <- glm(mpg~.,data=mtcars)

par(mfrow=c(2,2))
plot(gfit)


--- .class #id 
